Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}

### 2025-06-30 rapport.tex
minor chages

		In practice, the PRF used is AES specially because of it's hardware implementation which enables much faster tree generation than other PRF like SHA256 or other hash functions. The security of AES as a cryptographic PRF in a GGM tree generation has been studied in \cite{BCCG+24}.

>>>>

		In practice, most MPCitH schemes use hash functions with a salt value but the size of the entry must be $2\lambda$ to achieve $2^{\lambda}$ security bits. A recent work by Bui et al. studied the security of using the AES as the PRF. specially because of it's hardware implementation which enables much faster tree generation than other PRF like SHA256 or other hash functions. The security of AES as a cryptographic PRF in a GGM tree generation has been studied in \cite{BCCG+24}. Thanks to AES hardware implementation like Intel's AES-NI instruction set, schemes can be up to 50x times faster than versions using hash functions like SHA256.
